WIDS 2024 Final Presentation

### 2024-01-12 Documents/Presentation.qmd
revised pres

::: columns
::: {.column width="60%"}
-   Union and collective bargaining rates have collapsed over the last 40 years, although may just beginning to see a come back in the last two.
-   Southern states have much less union activity than northern and western states.
:::

::: {.column width="40%"}
![Plot 3](./Graph_Images/States_by_CB.png)
:::
:::

@@

::: columns
::: {.column width="60%"}
-   The country has generally grown more republican in the last 40 years, although data in the last 10 years show the pendulum might now be swinging the other way.
    -   Northern-midwest states have had the biggest shift to the right. New England is the only region that has seen a shift left.
:::

::: {.column width="40%"}
![Plot 4](./Graph_Images/House_by_year.png)
:::
:::

@@

::: columns
::: {.column width="60%"}
-   From the graph, it appears that a reduction in the amount of employees covered by a union leads to an increase in wages. However, for individual workers, being part of a union remains a way to increase wages.
-   We do not have data to compare wages and union rates by state, which would likely tell a different story.
:::

@@

::: columns
::: {.column width="60%"}
-   Our regression analysis shows that the south and north central regions in the United States are the main regions that have seen union membership rates and political leanings show increased correlation.
-   T-test between union and non union wages
    -   1980s: t = 22.846, df = 9.4096, p-value = 1.462e-09
        -   mean of x = 26.306; mean of y = 20.375
        -   95% CI: (5.347, 6.514)
    -   2010s: t = 9.5488, df = 15.629, p-value = 6.393e-08
        -   mean of x = 30.533; mean of y = 25.664
        -   95% CI: (3.786, 5.952)
:::

::: {.column width="40%"}
![Plot 8](./Graph_Images/Regression_plot.png)
:::
:::

>>>>

::: columns
::: {.column width="30%"}
-   Union and collective bargaining rates have collapsed over the last 40 years, although may just beginning to see a come back in the last two.
-   Southern states have much less union activity than northern and western states.
:::

::: {.column width="70%"}
![Plot 3](./Graph_Images/States_by_CB.png)
:::
:::

@@

::: columns
::: {.column width="30%"}
-   The country has generally grown more republican in the last 40 years, although data in the last 10 years show the pendulum might now be swinging the other way.
    -   Northern-midwest states have had the biggest shift to the right. New England is the only region that has seen a shift left.
:::

::: {.column width="70%"}
![Plot 4](./Graph_Images/House_by_year.png)
:::
:::

@@

::: columns
::: {.column width="60%"}
-   From the graph, it appears that a reduction in the amount of employees covered by a union leads to an increase in wages. However, for individual workers, being part of a union remains a way to increase wages.
-   This graph should not be interpreted as proving that decreased union activity leads to increased wages.
-   It is interesting that it appears that as union percentages decrease, the gap between union and non union data appears to be shrinking. Still, this correlation does not take into account the counts of workers in each group and other confounding variables could be effecting it as well.
:::

@@

::: columns
::: {.column width="70%"}
-   Our regression analysis shows that the south and north central regions in the United States are the main regions that have seen union membership rates and political leanings show increased correlation.
    - Plot 8 measures the regression estimates for the 10 SLR models that we ran. The increases in the 2010s grouping shows the increased politicization of unions in the U.S.
-   T-test between union and non union wages
    -   1980s: t = 22.846, df = 9.4096, p-value = 1.462e-09
        -   mean of x = 26.306; mean of y = 20.375
        -   95% CI: (5.347, 6.514)
    -   2010s: t = 9.5488, df = 15.629, p-value = 6.393e-08
        -   mean of x = 30.533; mean of y = 25.664
        -   95% CI: (3.786, 5.952)
:::

::: {.column width="30%"}
![Plot 8](./Graph_Images/Regression_plot.png)
:::
:::
